From Nested Virtualization Architecture \\To 2D Security Management for Distributed Clouds

### 2014-03-30 paper/draft.tex
Update cite uK
Qques corrections

%-- Relation entre MH et principes: 
%* MH naturally satisfy vertical design principles (DP1,DP3, DP4). 
MHs are particularly well adapted to sastisfy vertical design principles.
% Security:
%Pourquoi: 
For instance, MH design increases reliability as services crashing in user space may be restarted without bringing down the entire system (DP2).
%Fail-safe principle:
%Moving Finally, this extraction process drives to a more solid platform, considering that user-space crashes are generally not fatal for the entire system integrity. 
The attack surface is also lowered by the small TCB size, the minimal kernel only containing security-critical components and forming a last line of defense (DP3).
%The tiny core could be considered the only system-critical componente of the architecture and, due to its relative small dimension and the consequent minor attitude to vulnerabilities,it could represent the ``last line of defense''.
MH might also address some horizontal principles. 
%Interop principle:
%Qu'est ce que c'est:
``Personalities'' are concretely a set of processes handling specific functions running in user-space. Implementing such features outside the kernel makes it easier for each user to rely on different instances of such personalities running concurrently, possibly in a distributed manner (DP4).
%This process separation between users could enforce a straightforward mechanism to neutralize VM-to-VM attack from a malicious user. Moreover, user-space processes are easier to debug with commodity tools (GDB, valgrind).

@@

However, it fails to safisfy vertical design principles as TCB size is that of currently deployed NV architectures. The interest of other MH-based architectures will thus be to introduce isolation and privacy improvements by reducing the TCB, while still keeping horizontal features.

@@

This class of architecture may suffer from two types of limitations. First, nested VMX extensions must be exposed to the L1 hypervisor to let him ``nest'' another HVM guest. This requirement is implemented by GPHs like Xen and KVM, but usually not included in the key features to be provided by a MH: implementing nested VMX may be estimated to around 1KLoC, to be compared with the size of a typical MH (2-20 KLoC)~\cite{xmhf}.
More generally, the MH quest towards ever increasing minimalism could represent a serious limitation to preserving functions of existing platforms: the constraint of privileged code size may force MH developpers to drop some features considered as non-essential. This may apply to NV-related primitives, but also to other types of features. For instance, XMHF may only virtualize a single L1 instance at a time. While this may be acceptable if the platform objective to enforce strict resource access control in a single-provider private cloud, it hinders having a platform model enabling the user to run its own hypervisor as L1 to set up a self-service cloud independently from the underlying provider -- as in that case, multiple L1 hypervisors would need to run concurrently on the L0.

@@

%Super-cloud 
%The SUPERCLOUD will fulfill that vision with a two-level infrastructure:
The super-cloud has two main functions.
% Fonction North
% Fonctions 1: SUPERCLOUD Layer built SS cloud
% implementing the self-service security to build SSChe lower part of the SUPERCLOUD is be a distributed infrastructure will realize the distribute resource abstraction layer  and . It will implement the northbound, user-centric super-cloud API.
%The northbound, user-centric super-cloud API will implement self service security and dependability, allowing to build self-service clouds (SSC) where VM, network, and storage security may be personalized independently from the underlying provider. Such clouds may be defined at the service level to the full IaaS, relationships between SSC being flat or nested, also with complex trust relationships between sets of SSC according to the ecosystem relationships of the super-cloud providers providing the SSC.
Its northbound interface federates cloud resources in a provider-independent manner and enables to customize their security to realize the SSCs. While many orchestration architectures have been proposed at service or middleware levels (e.g., multi-Iaas platforms), our architecture aims to achieve federation at system-level to fully take advantage of underlying provider platform openness (if available) for finer-grained control and increased flexibility.
% Fonction South
% Fonction  2:
% The southbound, provider-centric super-cloud API will define a unified security and dependenability management plane of the compute, data, and network resources independently from providers. This may apply for B2B use cases to management of clouds of clouds but also to device-to-cloud scenarios if devices are considered, with possible extensions to the personal cloud for device-to-device scenarios, the SSC taking the form of personal cloud-based digital infospheres where security and dependability may be totally user-controlled.
% Also security management both vertically and horizontally.
% This means: providing vertically a cross-layer integrated vision of security of the cloud and SUPERCLOUD infrastructure; defining horizontally a security abstraction layer to achieve a homogeneous level of security across clouds independently from underlying provider mechanisms; and integrating both dimensions smoothly. This approach is key to providing a unified view of security of the SUPERCLOUD.

>>>>

%-- Relation entre MH et principes: 
%* MH naturally satisfy vertical design principles (DP1,DP3, DP4). 
MHs are particularly well adapted to satisfy vertical design principles.
% Security:
%Pourquoi: 
For instance, MH design increases reliability as services crashing in user space may be restarted without bringing down the entire system (DP2).
%Fail-safe principle:
%Moving Finally, this extraction process drives to a more solid platform, considering that user-space crashes are generally not fatal for the entire system integrity. 
The attack surface is also lowered by the small TCB size, the minimal kernel only containing security-critical components and forming a last line of defense (DP3).
%The tiny core could be considered the only system-critical componente of the architecture and, due to its relative small dimension and the consequent minor attitude to vulnerabilities,it could represent the ``last line of defense''.
MH might also address some horizontal principles. 
%Interop principle:
%Qu'est ce que c'est:
``Personalities'' are concretely a set of processes handling specific functions running in user-space. Implementing such features outside the kernel makes it easier for each user to rely on different instances of such personalities running concurrently, possibly in a distributed manner (DP4).
%This process separation between users could enforce a straightforward mechanism to neutralize VM-to-VM attack from a malicious user. Moreover, user-space processes are easier to debug with commodity tools (GDB, valgrind).

@@

However, it fails to satisfy vertical design principles as TCB size is that of currently deployed NV architectures. The interest of other MH-based architectures will thus be to introduce isolation and privacy improvements by reducing the TCB, while still keeping horizontal features.

@@

This class of architecture may suffer from two types of limitations. First, nested VMX extensions must be exposed to the L1 hypervisor to let him ``nest'' another HVM guest. This requirement is implemented by GPHs like Xen and KVM, but usually not included in the key features to be provided by a MH: implementing nested VMX may be estimated to around 1KLoC, to be compared with the size of a typical MH (2-20 KLoC)~\cite{xmhf}.
More generally, the MH quest towards ever increasing minimalism could represent a serious limitation to preserving functions of existing platforms: the constraint of privileged code size may force MH developers to drop some features considered as non-essential. This may apply to NV-related primitives, but also to other types of features. For instance, XMHF may only virtualize a single L1 instance at a time. While this may be acceptable if the platform objective to enforce strict resource access control in a single-provider private cloud, it hinders having a platform model enabling the user to run its own hypervisor as L1 to set up a self-service cloud independently from the underlying provider -- as in that case, multiple L1 hypervisors would need to run concurrently on the L0.

@@

%Super-cloud 
%The SUPERCLOUD will fulfill that vision with a two-level infrastructure:
The super-cloud has two main functions.
% Fonction North
% Fonctions 1: SUPERCLOUD Layer built SS cloud
% implementing the self-service security to build SSChe lower part of the SUPERCLOUD is be a distributed infrastructure will realize the distribute resource abstraction layer  and . It will implement the northbound, user-centric super-cloud API.
%The northbound, user-centric super-cloud API will implement self service security and dependability, allowing to build self-service clouds (SSC) where VM, network, and storage security may be personalized independently from the underlying provider. Such clouds may be defined at the service level to the full IaaS, relationships between SSC being flat or nested, also with complex trust relationships between sets of SSC according to the ecosystem relationships of the super-cloud providers providing the SSC.
Its northbound interface federates cloud resources in a provider-independent manner and enables to customize their security to realize the SSCs. While many orchestration architectures have been proposed at service or middleware levels (e.g., multi-IaaS platforms), our architecture aims to achieve federation at system-level to fully take advantage of underlying provider platform openness (if available) for finer-grained control and increased flexibility.
% Fonction South
% Fonction  2:
% The southbound, provider-centric super-cloud API will define a unified security and dependenability management plane of the compute, data, and network resources independently from providers. This may apply for B2B use cases to management of clouds of clouds but also to device-to-cloud scenarios if devices are considered, with possible extensions to the personal cloud for device-to-device scenarios, the SSC taking the form of personal cloud-based digital infospheres where security and dependability may be totally user-controlled.
% Also security management both vertically and horizontally.
% This means: providing vertically a cross-layer integrated vision of security of the cloud and SUPERCLOUD infrastructure; defining horizontally a security abstraction layer to achieve a homogeneous level of security across clouds independently from underlying provider mechanisms; and integrating both dimensions smoothly. This approach is key to providing a unified view of security of the SUPERCLOUD.
